che tipo di blockchain è e come utilizza i smart contracts

Flow, the blockchain for open worlds 
Flow is a fast, decentralized, and developer-friendly blockchain, designed as the foundation for a new generation of games, apps, and the digital assets that power them. 

It is based on a unique, multi-role architecture, and designed to scale without sharding, allowing for massive improvements in speed and throughput while preserving a developer-friendly, ACID-compliant environment.

Flow empowers developers to build thriving crypto- and crypto-enabled businesses. Applications on Flow can keep consumers in control of their own data; create new kinds of digital assets tradable on open markets accessible from anywhere in the world; and build open economies owned by the users that help make them valuable. 

Smart contracts on Flow can be assembled like Lego blocks to power apps serving billions of people, from basketball fans to businesses with mission-critical requirements.

There are four pillars that make Flow unique among existing blockchains: Multi-role architecture: Flow’s design is unique, allowing the network to scale to serve billions of users without sharding or reducing decentralization of consensus.

Resource-oriented programming: smart contracts on Flow are written in Cadence, an easier and safer programming language for crypto assets and apps. Developer ergonomics: from upgradeable smart contracts and built-in logging support to the Flow Emulator, this network is designed for results. 

Consumer onboarding: Flow was designed for mainstream consumers, with payment onramps catalyzing a safe and low-friction path from fiat to crypto.
While we originally started building Flow for our own use-cases, it has quickly become far bigger than us. Hundreds of developers in our discord and thousands around the world agree: we’re being something special here. Let’s build the future together!

Tool proposti da flow
Thin client

\begin{itemize}
    \item[] \textbf{Script}
    \item[] \textbf{Transactions}
    \item[] \textbf{Contract}
\end{itemize}

Tabella di confronto con Ethereum


\sezione{Cadence}
{capitoli/flow/cadence}

\sezione{Flow CLI}
{capitoli/flow/flow_cli}